Appendix: A missing guardrail---The minimal effect of election fraud on protest intensity in non-democracies

### 2022-11-16 Output/appendix.Rmd
Various changes to add new Nelda and MassMob variables; moved MassMob models to appendix 2

```{r setup, include = FALSE}
library(tidyverse)
library(countrycode)
library(readxl)
library(vdemdata)
library(lme4)
library(interplot)
library(lubridate)
library(summarytools)
library(stargazer)
library(cowplot)
library(pscl)
library(modelsummary)

@@

@@

>>>>

```{r setup, include = FALSE}
library(tidyverse)
library(countrycode)
library(readxl)
library(vdemdata)
library(lme4)
library(interplot)
library(lubridate)
library(summarytools)
library(stargazer)
library(cowplot)
library(pscl)
library(modelsummary)
library(MASS)

@@

## Changing participants from numeric category to text
nelda2.sub <- nelda2.sub %>% mutate(median.participants = round(median.participants))
nelda2.sub <- nelda2.sub %>% mutate(particpants_categorical = ifelse(is.na(median.participants)==T, NA, ifelse(median.participants == 1, "Less than 10",
                     ifelse(2, "10 to 99", ifelse(3, "100 to 999",
                                                  ifelse(4, "1000 to 9,999", ifelse(5, "Greater than 10,000", NA)))))))
nelda2.sub <- nelda2.sub %>% mutate(particpants_categorical = as.factor(particpants_categorical))

## Median particiants (MM) as factor

nelda2.sub <- nelda2.sub %>% mutate(median.participants.mm.post = as.factor(median.participants.mm.post))

@@

## Protest size (categories) using mass mobilization data

```{r}
## Econ grievance
dat <- ggpredict(model.size.griev2, terms = c("econ.crisis.nelda.1lag", "v2elirreg.inv"))
dat.sub <- dat %>% dplyr::filter(response.level == "0" | response.level == "2" | response.level == "4" | response.level == "6")
plot(dat.sub)

dat_max <- ggpredict(model.size.griev2, terms = c("econ.crisis.nelda.1lag", "v2elirreg.inv [-2.3, 3.2]"))
dat.sub <- dat %>% dplyr::filter(response.level == "0" | response.level == "3" | response.level == "6")
plot(dat.sub)
```

## Protest event quantity, MM version

```{r}
protest.cases.mm <- nelda2.sub %>% filter(n.events.massmob.post >= 1)

 ## This yields only 43 observations, do not run further.

model.n.base.mm <- glm.nb(n.events.massmob.post ~ jucon.1lag + legcon.1lag + gdpgro.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd + v2elirreg.inv  + presidential + inc.termlimit.num  + v2elintmon +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate, data = protest.cases %>% filter(gdpgro.1lag < 1))
summary(model.n.base.mm)
```
